---
title: "Problema 3.2"
author: "Hernan"
date: "24/11/2021"
output: html_notebook
---

<style type="text/css">
.main-container {
  max-width: 700px;
  margin-left: auto;
  margin-right: auto;
}
</style>

#Problema 3.2

```{r echo=FALSE, warning=FALSE, include=}
rm(list = ls())
graphics.off()

library(ggplot2)
library(leaps)
library(broom)
library(RobStatTM)
library(reshape2)
library(stringr)
```

#Descripcion
-----------

This dataset consists of features of handwritten numerals (`0'--`9')
extracted from a collection of Dutch utility maps. 200 patterns per
class (for a total of 2,000 patterns) have been digitized in  binary
images. These digits are represented in terms of the following six
feature sets (files): 

1. mfeat-fou: 76 Fourier coefficients of the character shapes; 
2. mfeat-fac: 216 profile correlations; 
3. mfeat-kar: 64 Karhunen-Love coefficients; 
4. mfeat-pix: 240 pixel averages in 2 x 3 windows; 
5. mfeat-zer: 47 Zernike moments; 
6. mfeat-mor: 6 morphological features. 


## Datos
```{r}
fou<-read.table("mfeat-fou.dat",header=FALSE)
fac<-read.table("mfeat-fac.dat",header=FALSE)
kar<-read.table("mfeat-kar.dat",header=FALSE)
pix<-read.table("mfeat-pix.dat",header=FALSE)
zer<-read.table("mfeat-zer.dat",header=FALSE)
mor<-read.table("mfeat-mor.dat",header=FALSE)
mor[,c(1:3)]<-as.factor(mor[,c(1:3)])
mfeat<-cbind(fou,fac,kar,pix,zer,mor)
colnames(mfeat)<-as.vector(seq(1,649,1))
class<-rep(0,2000)
class[(1:200)]<-0
class[(201:400)]<-1
class[(401:600)]<-2
class[(601:800)]<-3
class[(801:1000)]<-4
class[(1001:1200)]<-5
class[(1201:1400)]<-6
class[(1401:1600)]<-7
class[(1601:1800)]<-8
class[(1801:2000)]<-9
class<-as.factor(class)
datos<-cbind(mfeat,class)
```

#Train y Test
```{r}
set.seed(100)
n = nrow(datos)
trainIndex = sample(1:n, size = round(0.7*n), replace=FALSE)
ds.train = datos[trainIndex ,]
ds.test = datos[-trainIndex ,]

```


#Arbol
```{r}
library(rpart) 
model <- rpart( class ~ ., data=ds.train ) 
summary(model)
plot(model)
text(model)
```
